Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-01-18 code-tests.tex
Added hooks for thermal conduction tests, tweaked the main ms.tex file, and fixed a couple of typos in the outline.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Representative ray-tracing test}
\label{sec.tests.raytracing}
\red{(John)}
One test for MORAY: best/hardest one!

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Photo-evaporation of a dense clump}
\label{sec.tests.raytracing}
\red{(John)}
Photo-evaporation of a dense clump.  Tests ray tracing, specifically
the shadowing effects of the clump, and the hydrodynamic response of
the clump.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{Representative thermal conduction test}
\label{sec.tests.conduct}
\red{(Brian)}
One test for the thermal conduction (maybe 1 for isotropic, 1 for
anisotropic).
